---
title: "1.wrangling"
output: html_document
---
# Setup  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(tidyverse)
library(ggthemes)
library(readxl)
library(sf)
library(USAboundaries)

```

```{r theme}
theme_set(
  theme_excel()+
  theme(panel.grid = element_line(size=.1))
)
```

```{r df}
df <- read_excel("../data/meta2.xlsx", 
                 sheet = 1)
```

meta2.xlsx was added on June 2th and it has corrected missing  long/lat data for a few papers.  

# EDA  
```{r summary}
df %>% glimpse
```

```{r slice 1}
df %>%
  dplyr::select(study,
                resp,
                LRR,
                LRRyield)
```
need to replace . with NAs on LRRyield and elsewhere
bio and den can appear in same study (not exclusive)  

# Wrangling  
```{r df_w}
df_w <- df %>%
  # Changing . to NA
  mutate(across(everything(), 
                ~ifelse(. == ".",NA, .))) %>%
  # Changing some column types to numeric
  mutate(across(c(lat, long,
                  OM_pct, pH,
                  cc_plant.DOY,  
                  cc_plant.kgha, 
                  cc_term.DOY,
                  cc_bio_Mgha,
                  crop_plant.DOY,
                  term.plant.diff,
                  LRRyield
                  ),
                ~as.numeric(.)
                )) %>%
  mutate(weight = (sample_size * sample_size) / (sample_size + sample_size))
  
  
df_w %>% 
  glimpse
```


```{r separating resp}
df_w %>%
  filter(resp == "den") %>%
  rename(LRRden=LRR) %>%
  dplyr::select(-resp) %>%
  write_csv("../data/den_w.csv")

df_w %>%
  filter(resp == "bio") %>%
    rename(LRRbio=LRR) %>%
  dplyr::select(-resp) %>%
  write_csv("../data/bio_w.csv")
```


weed biomass under CC is 0.5 Mg/ha
weed biomass under no cc is 2 Mg/ha
```{r testing LRR results}
# CC reduced weed biomass
log(.5/2) #-1.386294

# No effect of CC on weed biomass
log(2/2) #0

# CC increased weed biomass
log(2/.5) #1.386294


```
for weed LRR, smaller/negative is better (CC suppressed weed).

for crop yield LRR, greater/positive is better (CC enhanced weed)









