---
title: "2.EDA"
output: html_document
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(tidyverse)
library(ggthemes)
library(readxl)
library(sf)
library(USAboundaries)
library(partykit)

```

```{r theme}
theme_set(
  theme_excel()+
    theme(panel.grid = element_line(size=.1))
)
```

```{r den_w}
den_w <- read_csv("../data/den_w.csv") %>%
  mutate_if(is.character, as.factor)

den_w
```

```{r checking weight}
df_w %>%
  ggplot(aes(x=wgt, y=weight))+
  geom_point()+
  geom_abline()

```

Weights didn't match, need to check with David how did he calculate weights.

# EDA

## Summaries

```{r den summary}
den_w %>%
  summary
```

```{r den NAs}
den_w %>%
  summarise_all(~ sum(is.na(.))) %>%
  pivot_longer(everything()) %>%
  mutate(propNA=round((value/139)*100,0)) %>%
  filter(propNA > 50)
```

Need to remove above variables from CIT.

```{r observations per state}
den_w %>%
  group_by(loc_state) %>%
  tally

```

```{r studies per state}
den_w %>%
  group_by(loc_state, study) %>%
  tally() %>%
  group_by(loc_state) %>%
  tally()

```

## Density distribution

```{r LRRden density plot}
den_w %>%
  ggplot(aes(x=LRRden))+
  geom_density()+
  geom_vline(xintercept = 0,
             color = "red")
```

```{r prop CC decreased den}
den_w %>%
  mutate(quad=ifelse(LRRden <= 0, "win", "loss")) %>%
  group_by(quad) %>%
  tally() %>%
  mutate(prop=round((n/139)*100,0))

```

```{r LRRyield density}
den_w %>%
  ggplot(aes(x=LRRyield))+
  geom_density()+
  geom_vline(xintercept = 0,
             color = "red")
```

```{r prop CC increased yield}
den_w %>%
  drop_na(LRRyield) %>%
  mutate(quad=ifelse(LRRyield > 0, "win", "loss")) %>%
  group_by(quad) %>%
  tally() %>%
  mutate(prop=round((n/101)*100,0))

```

## Density CIT

```{r den partykit}
den_w %>%
  dplyr::select(
    pub_year, 
    decade,
    study_duration,
    loc_state,
    lat, long, 
    soil_type,
    cc_spec,
    cc_type,
    tillage_sys,
    cc_plant.kgha,
    cc_pMETH,
    cc_term.METH,
    cc_term.METH2,
    add_herb,
    cc_bio_Mgha,
    crop,
    `weed type`,
    weed.sing.com,
    weed.spp,
    LRRden,
    #LRRyield
  ) %>%
  ctree(LRRden ~ .,
        data = .) %>%
  plot
```

```{r den vs pub_year}
den_w %>%
  ggplot(aes(x=pub_year, y=LRRden))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r den vs cc_bio_Mgha}
den_w %>%
  ggplot(aes(x=cc_bio_Mgha, y=LRRden))+
  geom_point()+
  geom_smooth(method="lm")+
  geom_vline(xintercept = 3.3)
```

```{r den vs study_duration}
den_w %>%
  ggplot(aes(x=study_duration, y=LRRden))+
  geom_point()+
  #geom_smooth(method="lm")
  geom_quantile(quantiles = c(.05, .5, .95))
```

## Density x yield quadrants CIT

```{r den vs yield}
den_w %>%
  filter(LRRyield > -2) %>% #one outlier
  ggplot(aes(x=LRRden, y=LRRyield))+
  geom_point(color="purple")+
  #geom_smooth()+
  geom_vline(xintercept = 0)+
  geom_hline(yintercept = 0)+
  geom_rug()

```

```{r den_q}
den_q <- den_w %>%
  mutate(quad=case_when(
    LRRden <= 0 & LRRyield > 0 ~ "w-w",
    LRRden <= 0 & LRRyield <= 0 ~ "w-l",
    LRRden > 0 & LRRyield > 0 ~ "l-w",
    LRRden > 0 & LRRyield <= 0 ~ "l-l"
  )) %>%
  mutate(quad=factor(quad))

den_q
```

```{r quadrant counts}
den_q %>%
  drop_na(LRRden, LRRyield) %>%
  group_by(quad) %>%
  tally() %>%
  mutate(prop=round((n/101)*100,0))

```

```{r den quad party}
den_q %>%
  dplyr::select(pub_year, 
    decade,
    study_duration,
    loc_state,
    lat, long, 
    soil_type,
    cc_spec,
    cc_type,
    tillage_sys,
    cc_plant.kgha,
    cc_pMETH,
    cc_term.METH,
    cc_term.METH2,
    add_herb,
    cc_bio_Mgha,
    crop,
    `weed type`,
    weed.sing.com,
    weed.spp,
    quad
    #LRRden,
    #LRRyield
  ) %>%
  drop_na(quad) %>%
  ctree(quad ~ .,
        data = .) %>%
  plot
```

## Spatial

```{r missing long but not lat}
den_q %>%
  distinct(pub_reference, long, lat) %>%
  filter(is.na(long) & !(is.na(lat)))
```

Smith et al., 2011\
Wells et al., 2013

Look into these above. How does it have lat but not long?

```{r den_sp}
den_sp <- den_q %>%
  drop_na(long, lat, quad) %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(value = 4326)
  

den_sp
```

```{r states}
states <- us_states() %>%
  dplyr::select(state_name, state_abbr) %>%
  filter(!(state_name %in% c("Hawaii", 
                             "Alaska",
                             "Puerto Rico"))) %>%
  st_transform(crs = 4326)

states
```

```{r map}
ggplot()+
  geom_sf(data=states)+
  geom_sf(data=den_sp)
```

```{r states filtered}
states_se <- states %>%
  filter(state_abbr %in% unique(den_sp$loc_state))

ggplot()+
  geom_sf(data=states_se)+
  geom_sf(data=den_sp #%>% st_jitter(.3)
          ,
          aes(color=quad),
          size=.7,
          show.legend = F)#+
  facet_wrap(~quad)

```

# Meeting May 27th

Look into pu_year vs den slope with and w/o earliest data, see magnitude and p-value. Look into cc_bio vs den, perhaps non-sig relationship \< 3.3 and significant when \> 3.3.

# To-do

Send CIT paper to David Sensitivity analysis (read/run)
