---
title: "figs"
output: html_document
date: '2022-06-23'
---

# Setup  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(USAboundaries) # pre-loaded maps package
library(ggpubr) # has nice themes
library(wesanderson) # colors
library(patchwork) #--multiple plots
library(ggthemes)
library(emmeans)
library(multcomp)
library(lme4)
library(sf)
library(partykit)
library(broom)
library(ggExtra)
library(ggpp)

```

```{r}
theme_set(
  theme_excel()+
    theme(panel.grid = element_line(size=0),
          plot.title = element_text(hjust = .5)
    )
)
```


```{r data}
# den_w
den_w <- read_csv("../data/den_w.csv") %>%
  mutate(LRR=LRRden,
         resp="den") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(-LRRden) #%>% #n=139
#drop_na(LRRyield) #n=101

# bio_w
bio_w <- read_csv("../data/bio_w.csv") %>%
  mutate(LRR=LRRbio,
         resp="bio") %>%
  dplyr::select(-LRRbio) #%>% #n=142
#drop_na(LRRyield) #n=83

# comb_w
comb_w <- den_w %>%
  bind_rows(bio_w) %>%
  mutate(quad=case_when(
    LRR <= 0 & LRRyield > 0 ~ "w-w",
    LRR <= 0 & LRRyield <= 0 ~ "w-l",
    LRR > 0 & LRRyield > 0 ~ "l-w",
    LRR > 0 & LRRyield <= 0 ~ "l-l"
  )) %>%
  mutate(across(where(is.character), factor))

comb_w
```

# Fig 1  - histograms  
To get the % reduction you back transform the natural log transformed value (e.g. LRRwden = -0.533 -> e^(-0.533) = 0.58 -> % reduction = 1- 0.58 = -42%). 

```{r den_hist }
options(contrasts = c("contr.sum", "contr.poly"))

em_den <- lmer(LRR ~ 1 + (1|pub_reference), data = den_w) %>%
  emmeans(~1) %>%
  as.data.frame() %>%
  rename(LRR=emmean)

nobs_den <- den_w %>%
  mutate(nobs=nrow(.)) %>%
  mutate(nstudy=length(unique(pub_reference))) %>%
  dplyr::select(nobs, nstudy) %>%
  distinct() %>%
  mutate(label = paste0(nobs, " (",nstudy,")")) %>%
  mutate(LRR=em_den$LRR) %>%
  mutate(eRR=exp(LRR)) %>%
  mutate(mean_pct=round((1-eRR)*100,0)) %>%
  mutate(mean_pct_lab=paste0(mean_pct,"%"))

den_hist <- ggplot(den_w, aes(x=LRR))+
  geom_density(fill="grey95")+
  geom_rect(data = em_den, aes(xmin = lower.CL, 
                               xmax = upper.CL, 
                               ymin=0, ymax=Inf),
            fill="purple",
            alpha=.6,
            inherit.aes = T)+
  geom_vline(xintercept = 0, color="forestgreen")+
  geom_vline(xintercept = em_den$LRR, linetype=2, color="blue")+
  labs(y="Kernel density",
       title="Weed density")+
  scale_x_continuous(breaks = c(-2,0,2))+
  scale_y_continuous(breaks = seq(0,0.6,.2),
                     limits = c(0,.6)
  )+
  geom_text_npc(npcx=0.1, npcy=.9, 
            label = paste0("mean: -",nobs_den$mean_pct_lab),
            hjust = 0, color="blue")+
  geom_text_npc(npcx=0.1, npcy=.85, label = paste0("n: ", nobs_den$label),
            hjust = 0, color="blue")+
  theme(axis.title.x = element_blank())

den_hist
```

```{r bio_hist }
options(contrasts = c("contr.sum", "contr.poly"))

em_bio <- lmer(LRR ~ 1 + (1|pub_reference), data = bio_w) %>%
  emmeans(~1) %>%
  as.data.frame() %>%
  rename(LRR=emmean)

nobs_bio <- bio_w %>%
  mutate(nobs=nrow(.)) %>%
  mutate(nstudy=length(unique(pub_reference))) %>%
  dplyr::select(nobs, nstudy) %>%
  distinct() %>%
  mutate(label = paste0(nobs, " (",nstudy,")")) %>%
  mutate(LRR=em_bio$LRR) %>%
  mutate(eRR=exp(LRR)) %>%
  mutate(mean_pct=round((1-eRR)*100,0)) %>%
  mutate(mean_pct_lab=paste0(mean_pct,"%"))

bio_hist <- ggplot(bio_w, aes(x=LRR))+
  geom_density(fill="grey95")+
  geom_rect(data = em_bio, aes(xmin = lower.CL, 
                               xmax = upper.CL, 
                               ymin=0, ymax=Inf),
            fill="purple",
            alpha=.6,
            inherit.aes = T)+
  geom_vline(xintercept = 0, color="forestgreen")+
  geom_vline(xintercept = em_bio$LRR, linetype=2, color="blue")+
  labs(y="Kernel density",
       #x= "Weed biomass\nlog response ratio"
       title="Weed biomass"
  )+
  #scale_y_continuous(breaks = seq(0,0.6,.2),
  #                   limits = c(0,.6))+
  scale_x_continuous(breaks = c(-2,0,2))+
    geom_text_npc(npcx=0.1, npcy=.9, 
            label = paste0("mean: -",nobs_bio$mean_pct_lab),
            hjust = 0, color="blue")+
  geom_text_npc(npcx=0.1, npcy=.85, label = paste0("n: ", nobs_bio$label),
            hjust = 0, color="blue")+
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()
  )

bio_hist

```

```{r yield_hist }
options(contrasts = c("contr.sum", "contr.poly"))

em_yield <- lmer(LRRyield ~ 1 + (1|pub_reference), data = comb_w3) %>%
  emmeans(~1) %>%
  as.data.frame() %>%
  rename(LRRyield=emmean)

nobs_yield <- comb_w3 %>%
  mutate(nobs=nrow(.)) %>%
  mutate(nstudy=length(unique(pub_reference))) %>%
  dplyr::select(nobs, nstudy) %>%
  distinct() %>%
  mutate(label = paste0(nobs, " (",nstudy,")")) %>%
  mutate(LRR=em_yield$LRR) %>%
  mutate(eRR=exp(LRR)) %>%
  mutate(mean_pct=round((eRR-1)*100,0)) %>%
  mutate(mean_pct_lab=paste0(mean_pct,"%"))

yield_hist <- ggplot(comb_w3, aes(x=LRRyield))+
  geom_density(fill="grey95")+
  geom_rect(data = em_yield, aes(xmin = lower.CL, 
                                 xmax = upper.CL, 
                                 ymin=0, ymax=Inf),
            fill="purple",
            alpha=.6,
            inherit.aes = T)+
  geom_vline(xintercept = 0, color="forestgreen")+
  geom_vline(xintercept = em_yield$LRR, linetype=2, color="blue")+
  labs(y="Kernel density",
       #x= "Yield\nlog response ratio"
       title = "Crop yield"
  )+
  #scale_y_continuous(breaks = seq(0,0.6,.2),
  #                   limits = c(0,.6)
  #)+
  scale_x_continuous(breaks = c(-2,0,2))+
      geom_text_npc(npcx=0.1, npcy=.9, 
            label = paste0("mean: ",nobs_yield$mean_pct_lab),
            hjust = 0, color="blue")+
  geom_text_npc(npcx=0.1, npcy=.85, label = paste0("n: ", nobs_yield$label),
            hjust = 0, color="blue")+
  theme(axis.title.y = element_blank(),
      axis.title.x = element_blank()
  )

yield_hist


```

```{r fig1}
(den_hist + bio_hist + yield_hist) /  
  wrap_elements(plot = grid::textGrob('Natural log of response (CC/no CC)'))+
  plot_layout(heights=c(15,1))



ggsave("../output/fig1.tiff",
       width = 8,
       height = 4)
```

# Fig 2 - map
```{r comb_sf}
comb_sf <- comb_w %>%
  drop_na(long, lat) %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(value = 4326) %>%
  #filter(resp == "den") %>%
  mutate(ref_loc=paste(pub_reference,"_",loc_citystate),
         ref_loc=factor(ref_loc))

comb_sf


comb_w %>%
  filter(is.na(long) | is.na(lat)) %>%
  distinct(study, pub_reference, loc_state)

comb_w %>%
  filter(loc_state == "FL") %>%
  dplyr::select(long, lat, LRR, LRRyield, resp)
```
```{r states}
states <- us_states() %>%
  dplyr::select(state_name, state_abbr) %>%
  filter(!(state_name %in% c("Hawaii", 
                             "Alaska",
                             "Puerto Rico"))) %>%
  st_transform(crs = 4326) %>%
  filter(state_abbr %in% unique(comb_sf$loc_state))


states
```
```{r nstudies_loc}
ncomp_loc <- comb_sf %>%
  dplyr::select(geometry) %>%
  distinct() %>%
  mutate(location=factor(1:nrow(.))) %>%
  st_join(comb_sf, join = st_equals, left=T) %>%
  group_by(location) %>%
  tally() %>%
  ungroup() %>%
  mutate(nf=factor(n)) %>%
  group_by(nf, n) %>%
  tally() %>%
  mutate(class=case_when(
    n >= 1 & n <= 5 ~ "1-5",
    n >= 6 & n <= 10 ~ "6-10",
    n >=12 & n <= 20 ~ "12-20",
    n >= 30 & n <= 43 ~ "30-43"
  ),
  class=factor(class,
               levels=c("1-5",
                        "6-10",
                        "12-20",
                        "30-43")))

ncomp_loc
```


```{r fig2}
library()
set.seed(6)
ggplot()+
  geom_sf(data=states, fill="gray90")+
  geom_sf(data=ncomp_loc,
          alpha=.7,
          shape=25,
          size=4,
          aes(fill=class))+
  scale_fill_viridis_d()+
  labs(fill="Num. of\ncomparisons")+
  guides(fill = guide_legend(override.aes = list(size = .4)))+
  theme(legend.position = c(.13,.25),
        axis.title = element_blank(),
        legend.background = element_rect(size=.1)
  )

ggsave("../output/fig2.tiff",
       height = 4,
       width = 6)
```

Color of points changed to be number of comparisons per location (instead of study).

# Fig 3 - CIT den  
```{r den_cit_w }
den_cit_w <- den_w %>%
  #filter(pub_year > 2001) %>%
  dplyr::select(
    pub_reference,
    pub_year, 
    decade,
    study_duration,
    loc_state,
    lat, long, 
    soil_type,
    cc_spec,
    cc_type,
    tillage_sys,
    cc_plant.kgha,
    cc_pMETH,
    cc_term.METH,
    cc_term.METH2,
    add_herb,
    cc_bio_Mgha,
    crop,
    `weed type`,
    weed.sing.com,
    weed.spp,
    LRR,
    #LRRyield
  )
```

```{r den_cit_mod}
den_cit_mod <- ctree(LRR ~ .-pub_reference,
                     data = den_cit_w,control = partykit::ctree_control(
                       maxsurrogate = 3,
                       saveinfo=T))

plot(den_cit_mod)
```
```{r}
surrogateinfo <- function(model, nodeids) {
  survarid <- 1:3
  df <- crossing(nodeids, survarid) %>%
    mutate(survarname=NA, level1=NA, level2=NA) %>%
    mutate(row=1:nrow(.))
  for (i in 1:nrow(df)) {
    surinfolist <- nodeapply(model, 
                             ids = df$nodeids[i], 
                             function(n) n$surrogates[[df$survarid[i]]])
    
    surinfo <- character_split(surinfolist[[1]], 
                               model.frame(model))
    
    survarname <- surinfo$name
    level1 <- surinfo$levels[[1]]
    level2 <- surinfo$levels[[2]]
    df$survarname[i] <- survarname
    df$level1[i] <- level1
    df$level2[i] <- level2
  }
  return(df)
}
```

```{r}
surrogateinfo(den_cit_mod, c(1)) %>%
  dplyr::select(survarname, level1, level2) %>%
  write_csv("../output/surrogates.csv")

```

```{r den_cit_w2}
den_cit_w2 <- den_cit_w %>%
  mutate(pred=predict(den_cit_mod, type="node"),
         pred=factor(pred))

den_cit_w2
```

```{r den_cit_lm}
den_cit_lm <- lmer(LRR ~ pred + (1|pub_reference),
                   data = den_cit_w2)

car::Anova(den_cit_lm, type=3)
```
```{r den_cit_means}
den_cit_means <- den_cit_lm %>%
  emmeans(~pred) %>%
  cld(reversed=T, adjust="none", Letter=letters) %>%
  as.data.frame() %>%
  mutate(id=as.numeric(as.character(pred))) %>%
  mutate(letter=trimws(.group))

den_cit_means
```

```{r den_cit_plot }
library(ggparty)

den_cit_plot <- ggparty(den_cit_mod, terminal_space = .33)+
  geom_edge()+
  # 1. Rounding edge numbers
  geom_edge_label()+
  # 2. Inner nodes label
  geom_node_label(aes(),
                  line_list = list(
                    aes(label = paste("Node", id)),
                    aes(label = splitvar),
                    aes(label = paste0(" N = ", nodesize,", p = ",round(p.value,3)))),
                  # set graphical parameters for each line
                  line_gpar = list(
                    list(size = 8, col = "black"),
                    list(size = 12, fontface = "bold"),
                    list(size = 8)),
                  ids = "inner")+
  
  # 3. Terminal nodes label
  geom_node_label(line_list = list(
    aes(label = paste0("Node ", id, ", N = ", nodesize))),
    # set graphical parameters for each line
    line_gpar = list(
      list(size = 8, col = "black")),
    ids = "terminal",
    nudge_x = .02,
    nudge_y = .023)+
  
  # 4. Terminal nodes plot
  geom_node_plot(gglist = 
                   list(
                     geom_hline(yintercept = 0, color="forestgreen"),
                     geom_boxplot(
                       aes(y = LRR,
                           x=1 
                           #fill = name
                       ), 
                       show.legend = F,
                       color="black",
                       alpha=.6),
                     geom_label(
                       data=den_cit_means,
                       aes(label=letter, 
                           x=1,
                           y=emmean
                       ),
                       label.padding = unit(.1,"lines")),
                     #scale_y_continuous(limits = c(-80,500), breaks = seq(0,500,100)),
                     theme(
                       axis.text.x = element_blank(),
                       axis.ticks.x = element_blank(),
                       axis.title.x = element_blank(),
                       plot.background = element_rect(fill="white")
                     ),
                     labs(y="Weed density LRR")
                   ),
                 # draw only one label for each axis
                 shared_axis_labels = TRUE,
                 # draw line between tree and legend
                 legend_separator = F)

den_cit_plot

ggsave(plot = den_cit_plot, bg = "white",
       filename = "../output/fig3.tiff", 
       width = 5, 
       height = 5)


```

# Fig 4 - Regression  
```{r den_lm}
den_lm <- lm(LRR ~ cc_bio_Mgha, 
             data = den_w %>%
               drop_na(LRR, cc_bio_Mgha)
)

den_lm 
```

```{r den_lm_aug}
den_lm_aug <- augment(den_lm) %>%
  mutate(.stdresid=resid(den_lm, type="pearson", scaled=T)) %>%
  mutate(LRR_cit=ifelse(cc_bio_Mgha<3.3, "<3.3", ">3.3"))

den_lm_aug
```

```{r cc_bio_50}
cc_bio_50 <- (-0.6931472 - coef(den_lm)[[1]])/coef(den_lm)[[2]]

cc_bio_50

```

```{r cit_th}
LRR_3.3 <- coef(den_lm)[[1]] + 3.3*coef(den_lm)[[2]]

LRR_3.3

1 - exp(LRR_3.3)
```

```{r fig4}
ggplot(den_lm_aug,
       aes(x=cc_bio_Mgha, y=LRR))+
  geom_point(aes(fill=LRR_cit), shape = 21, 
             alpha = .6, size = 3)+
  scale_fill_manual(values = c("#009E73", "#E69F00"))+
  geom_smooth(method = "lm", color="black")+
  geom_line(aes(y=.fitted), color="black")+
  geom_segment(x = cc_bio_50, xend = cc_bio_50,
               y = -0.6931472, yend = -3, color="white", linetype=3)+
  geom_segment(x = cc_bio_50, xend = -1,
               y = -0.6931472, yend = -0.6931472,
               color="white", linetype=3)+
  geom_point(x = cc_bio_50, y = -0.6931472, 
             fill="gray90",
             shape = 22,
             size=3)+
  labs(x=expression("Cover crop biomass (Mg" ~ha^-1* ")"),
       y="Weed density log response ratio",
       fill="CIT threshold")+
  scale_x_continuous(breaks = seq(0,14, 2))+
  theme(legend.position = c(.85,.8),
        legend.background = element_rect(fill="gray85", size=.1),
        legend.key = element_rect(fill = "gray85")
  )

ggsave(bg = "white",
       filename = "../output/fig4.tiff", 
       width = 6, 
       height = 4)
```

# Fig 5 - quadrants  
```{r comb_w2}
comb_w2 <- comb_w %>%
  drop_na(LRR, LRRyield) %>%
  mutate(resp=ifelse(resp == "bio", "biomass", "density"))

comb_w2

```
```{r quad_prop}
quad_prop <- comb_w2 %>%
  mutate(N=length(LRR)) %>%
  mutate(quad=case_when(
    LRR <= 0 & LRRyield > 0 ~ "W-W",
    LRR <= 0 & LRRyield <= 0 ~ "W-L",
    LRR > 0 & LRRyield > 0 ~ "L-W",
    LRR > 0 & LRRyield <= 0 ~ "L-L"
  )) %>%
  mutate(quad=factor(quad)) %>%
  group_by(quad, N) %>%
  summarise(n=length(quad)) %>%
  mutate(prop=round((n/N)*100,0)) %>%
  mutate(prop_lab=paste0(quad,"\n",prop,"%")) %>%
  ungroup() %>%
  mutate(x=c(1, 1, -2, -2),
         y=c(-2,2,-2,2))

quad_prop
```

```{r quad_resp_prop}
quad_resp_prop <- comb_w2 %>%
  mutate(quad=case_when(
    LRR <= 0 & LRRyield > 0 ~ "W-W",
    LRR <= 0 & LRRyield <= 0 ~ "W-L",
    LRR > 0 & LRRyield > 0 ~ "L-W",
    LRR > 0 & LRRyield <= 0 ~ "L-L"
  )) %>%
  mutate(quad=factor(quad)) %>%
  group_by(resp) %>%
  mutate(N=length(LRR)) %>%
  group_by(quad, resp, N) %>%
  summarise(n=length(quad)) %>%
  mutate(prop=round((n/N)*100,0)) %>%
  mutate(prop_lab=paste0(prop,"%")) %>%
  ungroup() %>%
  mutate(x=c(1,1, 1,1, -2,-2, -2,-2),
         y=c(-2,-2,2,2,-2,-2,2,2)) %>%
  dplyr::select(quad, prop_lab, x, y, resp) %>%
  spread(resp, prop_lab) %>%
  mutate(lab=paste0("<i style='color:#D55E00;'>",biomass,"</i>, <i style='color:#0072B2;'>",density,"</i>"))

quad_resp_prop
```

```{r quad_plot}
quad_plot <- ggplot(comb_w2, aes(x=LRR, y=LRRyield, 
                                 color=resp,
                                 fill = resp))+
  geom_vline(xintercept = 0)+
  geom_hline(yintercept = 0)+
  geom_point(alpha = .6, 
             size = 2)+
  scale_color_manual(values = c("#D55E00","#0072B2"))+
  scale_fill_manual(values = c("#D55E00","#0072B2"))+
  labs(y="Crop yield log response ratio",
       x="Weed log response ratio")+
  geom_text(data = quad_prop, aes(x=x, y=y, label=prop_lab),
            inherit.aes = F)+
  ggtext::geom_richtext(data = quad_resp_prop, 
                        aes(x=x, y=y, label=lab),
                        inherit.aes = F,
                        fill=NA,
                        label.color=NA,
                        size=3,
                        nudge_y = -.8)+
  
  theme(legend.position = c(.91,.905),
        legend.title = element_blank(),
        legend.background = element_rect(fill="gray85", size=.1),
        legend.key = element_rect(fill = "gray85", size=1),
        legend.margin = margin(0.2,0.2,0.2,0.2),
        legend.spacing.y = unit(.001, "cm")
  )

ggMarginal(quad_plot, groupColour = T,  groupFill = T)

ggsave(bg = "white",
       filename = "../output/fig5.tiff", 
       width = 6, 
       height = 4)
```



# Summary table  
```{r comb_w3 }
comb_w3 <- den_w %>%
  rename(LRRden=LRR) %>%
  dplyr::select(-resp) %>%
  full_join(bio_w %>%
              rename(LRRbio=LRR) %>%
  dplyr::select(-resp)) %>% #241
  dplyr::select(pub_reference,
    pub_year,
                study_duration,
                soil_type,
                pH,
                cc_spec,
                cc_type,
                tillage_sys,
                cc_term.METH,
                add_herb,
                cc_bio_Mgha,
                crop,
                weed_type=`weed type`,
                weed.sing.com,
                LRRyield,
                LRRden, LRRbio
  ) %>%
    mutate(across(where(is.character), factor))


comb_w3
```

```{r comb_w3_n}
comb_w3_n <- comb_w3 %>%
  dplyr::select_if(is.numeric) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  nest() %>%
  mutate(sum=map(data,
                 ~.x %>%
                   drop_na() %>%
                   summarise(N = length(value),
                             min = round(min(value),1),
                             mean = round(mean(value),2),
                             median = round(median(value),1),
                             max = round(max(value),1),
                             sd = round(sd(value),1),
                             cv = sd/mean
                   )
  )) %>%
  unnest(sum) %>%
  dplyr::select(-data) 

comb_w3_n

comb_w3_n %>%
  write_csv("../output/sumtable_num.csv")

```

```{r comb_w3_c}
comb_w3_c <- comb_w3 %>%
  dplyr::select_if(is.factor) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  nest() %>%
  mutate(sum=map(data,
                 ~.x %>%
                   drop_na(value) %>%
                   group_by(value) %>%
                   tally() %>%
                   mutate(N=sum(n))
  )) %>%
  unnest(sum) %>%
  dplyr::select(-data)

comb_w3_c

comb_w3_c %>%
  write_csv("../output/sumtable_cat.csv")

```


# Figures  
- Histograms for overall effects (Leo) (DONE)
- Map (Leo) DONE
- CIT for density (Leo, run anova, add letters, make a nice CIT) (DONE)
- regression LRRdensity vs. cc_biomass (try LP, QP, poisson, see what happens) (DONE)
- quadrants (Leo) (DONE)
- Table with summary for all descriptors (DONE)


- Write about methods  
- Remake other 2 figures to keep format consistent (DONE)
- Sensitivity
- Bias

Sofia and Ceren (Jeren)



# Meeting June 29th 
```{r}
den_w %>%
  drop_na(cc_bio_Mgha) %>%
  mutate(cit_th=ifelse(cc_bio_Mgha>3.3,">3.3","<3.3")) %>%
  ggplot(aes(x=pub_year, y=LRR))+
  geom_point(aes(color=cit_th), alpha=.6, size=2)+
  #geom_smooth(method="lm")+
  geom_smooth(aes(color=cit_th), method="lm")
facet_wrap(~cc_term.METH2)
```

